---
title: "2022_08_09_Simulation_1_Paramutations"
author: Almorò Scarpa
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction


### Initial conditions:

A population of 1000, 5 chromosomes of size 10 Mb, 5 piRNA clusters of size 300 Kb and an initial number of TEs in the population equal to 100.

We used 300 replicates for each simulation.

## Materials & Methods
version: invadego0.2.1

### Commands for the simulation:

```{bash, eval=FALSE}
folder="/Users/ascarpa/Paramutations_TEs/Simulation"
tool="/Users/ascarpa/invade-invadego/invadego022"

$tool --N 1000 --gen 5000 --genome mb:10,10,10,10,10 --rr 4,4,4,4,4 --rep 100 --u 0.1 --basepop 100 --paramutation 10:1,3,5 --trigger 1000:1 --steps 20 --sampleid p30_0.1 > $folder/2022_08_09_simulation_2_1

$tool --N 1000 --gen 5000 --genome mb:10,10,10,10,10 --rr 4,4,4,4,4 --rep 100 --u 0.1 --basepop 100 --paramutation 10:1,3,5 --trigger 100:1 --steps 20 --sampleid p30_1 > $folder/2022_08_09_simulation_2_2

$tool --N 1000 --gen 5000 --genome mb:10,10,10,10,10 --rr 4,4,4,4,4 --rep 100 --u 0.1 --basepop 100 --paramutation 10:1,3,5 --trigger 10:1 --steps 20 --sampleid p30_10 > $folder/2022_08_09_simulation_2_3

$tool --N 1000 --gen 5000 --genome mb:10,10,10,10,10 --rr 4,4,4,4,4 --rep 100 --u 0.1 --basepop 100 --paramutation 10:1,3,5 --trigger 1:0 --steps 20 --sampleid p30_100 > $folder/2022_08_09_simulation_2_4

cat 2022_08_09_simulation_2_1 2022_08_09_simulation_2_2 2022_08_09_simulation_2_3 2022_08_09_simulation_2_4 |grep -v "^Invade"|grep -v "^#" > 2022_08_09_Simulation_2_Trigger
```


### Visualization in R

Setting the environment
``` {r, message = FALSE}

```

Visualization: comparing the simulations with the prediction
```{r, warning=FALSE}

```


## Conclusions
